---
title: "My R Markdown Primer"
author: "Gabriel Myles"
output: html_document
---

# Introduction

This document demonstrates the basics of R Markdown, including text formatting, embedded R code, and simple LaTeX math. R Markdown allows you to mix narrative text and code in a single reproducible document.

R Markdown documents use markdown syntax for formatting. You can include **bold text**, *italics*, lists, headers, and more.

# Narrative Section

R Markdown helps combine analysis and explanation. Instead of writing your report separately from your code, everything stays in one place and updates automatically when you knit the document.

# Math Example

Here is an inline math expression: $\alpha + \beta = \gamma$.

And here is a displayed equation:

$$
x = y^2 + 3y + 2
$$

# Code Chunks

Below are examples of executable R code chunks.

## Chunk 1: Load a Dataset

```{r}
data(iris)
head(iris)
```

## Chunk 2: Simple Summary

```{r}
summary(iris$Sepal.Length)
```

## Chunk 3: Plot (ggplot2)

```{r}
library(ggplot2)

ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point() +
  theme_minimal()
```

# Conclusion

Using R Markdown makes it easy to produce clean, reproducible reports that include text, code, results, and graphics. Compared to writing a plain report, this workflow saves time and reduces errors because the output updates automatically whenever the code changes.
